### 2020-11-06 Thesis-Chapter4-Arguments.tex
Work on EA types argmaps
Finish chapter 4, argument maps

\begin{figure}[h]
  \centering\CaptionFontSize
  \includegraphics[width=\linewidth]{arguments/build/comprehensive.classes.pdf}
  \caption{Classes of EA}
  \label{fig-arg-classes}
\end{figure}

% What properties would good EA have?
% easy for LEAs to use? hard? expensive? voluntary? unable to be used for mass surveillance? transparent (attempts are
%   visible)? alignment of values with security (e.g. discourages bug hoarding)? adaptable (since solution won't be
%   permanent, either technically or according to collective will as things change rozenshtein_wicked_2018)? suited to
%   rules and principles (matyas_incommensurability_2018)?

\section{Specific Proposals}

\begin{figure}[h]
  \centering\CaptionFontSize
  \includegraphics[width=\linewidth]{arguments/build/comprehensive.proposals.pdf}
  \caption{EA Proposals}
  \label{fig-arg-proposals}
\end{figure}

% See: committee_decrypting_2018, group_2019, various proposals

>>>>

\myfig{fig-arg-classes} lists several classes of \ac{EA} and arguments in their favor and disfavor. Classes applicable
to both \ac{DIM} and \ac{DAR} include using weak cryptography, trusted-party key escrow, and distributed key escrow.
Using cryptographic puzzles and adding a ghost user apply to the case of \ac{DIM}, and device key escrow applies to
\ac{DAR}.

\begin{sidewaysfigure}[p!]
  \centering\CaptionFontSize
  \includegraphics[width=\linewidth]{arguments/build/comprehensive.classes.pdf}
  \caption{Classes of EA}
  \label{fig-arg-classes}
\end{sidewaysfigure}

It should be noted that the \ac{argmap} format works best when displaying the debate surrounding a single conclusion or
proposal. That leaves room for points and counterpoints to be elaborated in detail, as opposed to creating a tangled web
of un-elaborated connections. For the sake of brevity, this thesis considers \ac{EA}'s alternatives and variations at a
high level. For an excellent, thorough discussion of \ac{EA}'s alternatives and variations, see the National Academies
of Sciences, Engineering, and Medicine's 2018 report titled \ii{Decrypting the Encryption Debate: A Framework for
Decision Makers} \cite{committee_decrypting_2018}.

The first \ac{EA} class is to simply use weak cryptographic ciphers or short encryption keys. This was the approach
taken before \ac{the-cw1}, when strong cryptography was not highly available and subject to export controls. No party
seriously supports this approach today, as it is irreconcilably contradictory to strong security on many levels.

Trusted-party key escrow relies on the an entity or small group of entities to store a key or key recovery information.
There are a wide variety of implementations \cite{denning_taxonomy_1996}, but by definition this class of \ac{EA}
carries a crushing weakness: the centralization of extremely sensitive information. Proponents argue that software
companies' protection of code-signing keys in hardware security modules is evidence that they can protect such sensitive
data when needed \cite{ozzie_2018}, but opponents point out that such keys are accessed quite rarely used (especially
when compared to the likely frequency of \ac{EA} requests) and yet they indeed still leak \cite{green_2018}. Once the
escrowed keys are stolen, as they inevitably would be, every device or message encrypted with them would be at risk.
This is an example of a case when the \ac{argmap} format doesn't do an argument justice---the argument against any
centralized access mechanism is extremely powerful.

Distributed key escrow differs from trusted-party in that it takes strong steps to remove centralized trust. This is
achieved by using distributed systems to make key extraction difficult and inherently public \cite{phan_key_2017}
\cite{servan_schreiber_jje_2020}. If the distributed protocols hold up, one advantage of distribution is that this
approach is that it is more likely to fail by making data unrecoverable than by making unintended data vulnerable,
though more research into this area is needed. The downside of these systems is their complexity, which could make it
costly and hard to update.

One class of \ac{DIM} \ac{EA} involves using strong cryptography, but including cryptographic puzzle pieces as message
metadata. These pieces are designed to reveal the encryption key after the surveiller spends considerable computational
power \cite{bellare_translucent_1996} \cite{wright_crypto_2018}. This approach precludes \ii{mass} surveillance, but it
also enables \ii{arbitrary} surveillance by anyone with enough computing power. Use in common cases would be impractical
due to high cost, but use in high profile cases would be less effective due to the likelihood of \ac{EA} workarounds
employed by sophisticated adversaries. Additionally, the calibration of puzzle difficulty is dependent on the state of
computing. Since opponents can record data and decrypt it later when computational capabilities have changed, the data
becomes steadily less secure over time.

Another \ac{DIM} proposal is to ``conference call'' authorities in as a ghost participant in the conversation. It was
notably suggested by \ac{GCHQ} officials Ian Levy and Crispin Robinson \cite{levy_robinson_2018}. Their writeup begins
with some core ideas of this thesis:

\begin{displayquote}
In any discussion of cyber security, details matter.

Unfortunately, it's the details that are missing from the discussion around lawful access to commodity end-to-end
encrypted services and devices (often called the ``going dark'' problem). Without details, the problem is debated as a
purely academic abstraction concerning security, liberty, and the role of government.

There is a better way that doesn’t involve, on one side, various governments, and on the other side lawyers,
philosophers, and vendors' PR departments continuing to shout at each other. If we can get all parties to look at some
actual detail, some practices and proposals---without asking anyone to compromise on things they fundamentally believe
in---we might get somewhere.
\cite{levy_robinson_2018}
\end{displayquote}

As goodwill participants in the conversation, trying to spur discussion around specific proposals ``without people being
vilified for having a point of view or daring to work on this as a problem,'' they deserve credit and thanks.

Unfortunately, the proposal they share is indeed problematic. The ghost user proposal prides itself on not compromising
strong encryption. This is a good property, but compromising a messaging app's authorization protocol is as dangerous as
compromising its encryption \cite{callas_1_2019}. Fundamentally, it suffers from the same weakness as trusted-party key
escrow; the introduction of an authorization vulnerability in the messaging service provider's platform amounts to a
highly risky centralization of access capability \cite{schneier_ghost_2019}. It has the same nature, if a different
form, as rejected key escrow proposals.

Finally, one \ac{DAR}-specific \ac{EA} class is device key escrow. In this scheme, key recovery material exists on the
device itself. While not necessary to classify as device key escrow, most of these proposals include physical possession
requirements and additionally ``brick'' the device or make it absolutely clear that \ac{EA} has been performed
\cite{savage_lawful_2018} \cite{ozzie_2018}. Such features precludes mass surveillance and ensure transparency to the
device user. This approach relies on secure hardware and a method of authorizing the recovery request to the device
itself. The authentication step can be paired with other \ac{EA} strategies, such as engaging with trusted-parties or
distributed systems. This is where the device escrow shows its weaknesses. Secure hardware enclaves, though improving,
are not totally reliable, and authentication to the hardware device is susceptible to the same attacks as traditional
escrow \ac{EA}.

Device key escrow's greatest weaknesses, however, still represent signs of progress. It is true that it relies on a
device's secure enclave, but devices already do---it is the same hardware devices that manages device unlock and
encryption functionality in the first place. Adding functionality increases the attack surface, but it does not add a
completely new threat vector. It is also true that the process is subject to the same problems as traditional key escrow
after the device has been obtained, but that is precisely the progress that has been made---\ii{after the device has
been obtained}. Leveraging advances in secure hardware design has meaningfully changed the \ac{EA} risk profile.

In 2019, Carnegie Mellon assembled an ideologically diverse group of policy and security experts to engage in the kind
of cross-disciplinary debate this thesis advocates. After considering all the technical corners of the situation, their
report goes into detail on why \ac{EA} for domestic law enforcement (i.e., common cases instead of sophisticated
adversaries) focusing on \ac{DAR} in mobile phones using device key escrow requiring physical access is the most
tractable technical case to consider \cite{group_2019}. By now it should be clear why: traditional investigation mixed
with a dose of lawful hacking is best suited for advanced opponents, and device key escrow represents actual progress as
a path towards lower-risk \ac{EA}.

Device key escrow still has a long way to go. There are few proposals, what few there are are high level, and questions
of scaling and administration have not been addressed. However, as \ac{incrementalism}'s Lindblom and even \ac{GCHQ}'s
Levy and Robinson have pointed out, focusing on specific proposals has the opportunity to identify mutually agreeable
solutions---or at least refine the problem understanding enough that the next round of debate can be better informed.

It is this task that we turn to next. The following chapter analyzes one particular device-escrow proposal in moderate
detail, Stefan Savage's ``Lawful Device Access without Mass Surveillance Risk: A Technical Design Discussion''
\cite{savage_lawful_2018}.

% \section{Specific Proposals}
%% NOTE: not worth going into this section. Just describe a few and go straight to one of the most interesting.

% \begin{figure}[h]
%   \centering\CaptionFontSize
%   \includegraphics[width=\linewidth]{arguments/build/comprehensive.proposals.pdf}
%   \caption{EA Proposals}
%   \label{fig-arg-proposals}
% \end{figure}

% % See: committee_decrypting_2018, group_2019, various proposals

### 2020-11-06 Thesis-Glossary.tex
Write contributing factors map section
Finish chapter 4, argument maps

\newterm{horsemen}{the Four Horsemen}{
    Four reasons that governments and law enforcement agencies use to undercut public support for strong encryption. The
    four horsemen are terrorists, pedophiles (child pornographers), drug dealers (and traffickers), and money launderers
    (or kidnappers)
}
\newterm{horsemen-full}{the Four Horsemen of the Infocalypse}{The long name for ``The Four Horsemen''}

@@

% Start acronyms
\newabbreviation{AECA}{AECA}{Arms Export Control Act}
\newabbreviation{AV}{AV}{anti-virus}
\newabbreviation{AWA}{AWA}{All Writs Act}
\newabbreviation{CALEA}{CALEA}{Communications Assistance for Law Enforcement Act}
\newabbreviation{CESA}{CESA}{Cyberspace Electronic Security Act}
\newabbreviation{CFAA}{CFAA}{Computer Fraud and Abuse Act}
\newabbreviation{CP}{CP}{child pornography}
\newabbreviation{CSAM}{CSAM}{child sexual abuse material}
\newabbreviation{CSAV}{CSAV}{computer supported argument visualization}
\newabbreviation{DE}{DE}{device encryption}
\newabbreviation{DFD}{DFD}{data flow diagram}
\newabbreviation{DIM}{DIM}{data in motion}
\newabbreviation{DAR}{DAR}{data at rest}
\newabbreviation{E2E}{E2E}{end to end}
\newabbreviation{E2EE}{E2EE}{end to end encryption}
\newabbreviation{EA}{EA}{exceptional access}
\newabbreviation{ECPA}{ECPA}{Electronic Communications Privacy Act}
\newabbreviation{ED}{ED}{ephemeral data}
\newabbreviation{FBI}{FBI}{Federal Bureau of Investigation}
\newabbreviation{FISA}{FISA}{Foreign Intelligence Surveillance Act}
\newabbreviation{FISAAA}{FISAAA}{FISA Amendments Act}
\newabbreviation{FISC}{FISC}{Foreign Intelligence Surveillance Court}
\newabbreviation{IBIS}{IBIS}{issue-based information system}
\newabbreviation{ITAR}{ITAR}{International Traffic in Arms Regulations}
\newabbreviation{KEK}{KEK}{key encrypting key}
\newabbreviation{LE}{LE}{law enforcement}
\newabbreviation{LEA}{LEA}{law enforcement agency}
\newabbreviation{LEO}{LEO}{law enforcement officer}
\newabbreviation{NED}{NED}{non-ephemeral data}
\newabbreviation{NSA}{NSA}{National Security Agency}
\newabbreviation{NSL}{NSL}{National Security Letter}
\newabbreviation{PAA}{PAA}{Protect America Act}
\newabbreviation{PGP}{PGP}{Pretty Good Privacy}
\newabbreviation{PIN}{PIN}{personal identification number}
\newabbreviation{PKI}{PKI}{public key infrastructure}
\newabbreviation{PW}{PW}{password}
\newabbreviation{SE}{SE}{strong encryption}
\newabbreviation{SSO}{SSO}{single sign-on}
\newabbreviation{TLS}{TLS}{Transport Layer Security}
\newabbreviation{VPN}{VPN}{virtual private network}
% End acronyms

>>>>

\newterm{horsemen}{Four Horsemen}{
    Four reasons that governments and law enforcement agencies use to undercut public support for strong encryption. The
    four horsemen are terrorists, pedophiles (child pornographers), drug dealers (and traffickers), and money launderers
    (or kidnappers)
}
\newterm{horsemen-full}{the Four Horsemen of the Infocalypse}{The long name for ``The Four Horsemen''}

@@

% Start acronyms
\newabbreviation{AECA}{AECA}{Arms Export Control Act}
\newabbreviation{AV}{AV}{anti-virus}
\newabbreviation{AWA}{AWA}{All Writs Act}
\newabbreviation{CALEA}{CALEA}{Communications Assistance for Law Enforcement Act}
\newabbreviation{CESA}{CESA}{Cyberspace Electronic Security Act}
\newabbreviation{CFAA}{CFAA}{Computer Fraud and Abuse Act}
\newabbreviation{CP}{CP}{child pornography}
\newabbreviation{CSAM}{CSAM}{child sexual abuse material}
\newabbreviation{CSAV}{CSAV}{computer supported argument visualization}
\newabbreviation{DE}{DE}{device encryption}
\newabbreviation{DFD}{DFD}{data flow diagram}
\newabbreviation{DIM}{DIM}{data in motion}
\newabbreviation{DAR}{DAR}{data at rest}
\newabbreviation{E2E}{E2E}{end to end}
\newabbreviation{E2EE}{E2EE}{end to end encryption}
\newabbreviation{EA}{EA}{exceptional access}
\newabbreviation{ECPA}{ECPA}{Electronic Communications Privacy Act}
\newabbreviation{ED}{ED}{ephemeral data}
\newabbreviation{FBI}{FBI}{Federal Bureau of Investigation}
\newabbreviation{FISA}{FISA}{Foreign Intelligence Surveillance Act}
\newabbreviation{FISAAA}{FISAAA}{FISA Amendments Act}
\newabbreviation{FISC}{FISC}{Foreign Intelligence Surveillance Court}
\newabbreviation{GCHQ}{GCHQ}{(UK) Government Communications Headquarters}
\newabbreviation{IBIS}{IBIS}{issue-based information system}
\newabbreviation{ITAR}{ITAR}{International Traffic in Arms Regulations}
\newabbreviation{KEK}{KEK}{key encrypting key}
\newabbreviation{LE}{LE}{law enforcement}
\newabbreviation{LEA}{LEA}{law enforcement agency}
\newabbreviation{LEO}{LEO}{law enforcement officer}
\newabbreviation{NED}{NED}{non-ephemeral data}
\newabbreviation{NSA}{NSA}{National Security Agency}
\newabbreviation{NSL}{NSL}{National Security Letter}
\newabbreviation{PAA}{PAA}{Protect America Act}
\newabbreviation{PGP}{PGP}{Pretty Good Privacy}
\newabbreviation{PIN}{PIN}{personal identification number}
\newabbreviation{PKI}{PKI}{public key infrastructure}
\newabbreviation{PW}{PW}{password}
\newabbreviation{SE}{SE}{strong encryption}
\newabbreviation{SSO}{SSO}{single sign-on}
\newabbreviation{TLS}{TLS}{Transport Layer Security}
\newabbreviation{VPN}{VPN}{virtual private network}
% End acronyms
